Staged Abstract Interpreters

### 2019-03-21 paper/10_intro.tex
replace Id with IdM

\paragraph{Abstraction, Abstraction, and Abstraction}
To enable such flexibility between different semantics, we extensively use
abstract type members over multiple abstractions, which can be later instantiated.

\begin{itemize}
\item Monadic abstractions, which encapsulate the following two abstractions.
  The interpreter itself is written in monadic form
  \cite{Steele:1994:BIC:174675.178068, DBLP:conf/popl/LiangHJ95,
  DBLP:journals/pacmpl/DaraisLNH17, Sergey:2013:MAI:2491956.2491979}, by plugging
  different monads, the underlying semantics of the interpreter is changed.
  \todo{mention that direct-style also works?}
\item Env-store-value abstractions, which control whether the interpreter
  behaves as a concrete interpreter or an abstract interpreter.
  The environments, stores and values declared in the generic interpreter are
  abstract types; we also define several abstract methods that manipulate
  environments or stores.
  As shown by the AAM approach \cite{DBLP:journals/jfp/HornM12,
  DBLP:conf/icfp/HornM10}, if we widen the values to abstract domains (such as
  intervals) and refactor the store to a mapping from finite addresses to sets of
  values, we can derive a computable and sound abstract interpreter.
\item Binding-time abstractions, which control whether the interpreter produces
  values or residual programs. The binding-times differentiate whether the
  data is known statically or dynamically. Unsurprisingly, such binding-time
  information can be encoded into higher-kinded types \todo{cite FTPE, stage poly}.
\end{itemize}

>>>>

\paragraph{Abstraction, Abstraction, and Abstraction}
To enable such flexibility between different semantics, we combine generic 
programming and generative programming, and extensively use abstract type members 
over multiple abstractions, which can be later instantiated.

\begin{itemize}
\item Monadic abstractions, which encapsulate the following two abstractions.
  The interpreter itself is written in monadic form
  \cite{Steele:1994:BIC:174675.178068, DBLP:conf/popl/LiangHJ95,
  DBLP:journals/pacmpl/DaraisLNH17, Sergey:2013:MAI:2491956.2491979}, by plugging
  different monads, the underlying semantics of the interpreter is changed.
  \todo{mention that direct-style also works?}
\item Env-store-value abstractions, which control whether the interpreter
  behaves as a concrete interpreter or an abstract interpreter.
  The environments, stores and values declared in the generic interpreter are
  abstract types; we also define several abstract methods that manipulate
  environments or stores.
  As shown by the AAM approach \cite{DBLP:journals/jfp/HornM12,
  DBLP:conf/icfp/HornM10}, if we widen the values to abstract domains (such as
  intervals) and refactor the store to a mapping from finite addresses to sets of
  values, we can derive a computable and sound abstract interpreter.
\item Binding-time abstractions, which control whether the interpreter produces
  values or generates code. The binding-times differentiate whether data are 
  known statically or dynamically. Unsurprisingly, such binding-time
  information can be encoded into higher-kinded types 
    \cite{DBLP:journals/jfp/CaretteKS09, Ofenbeck:2017:SGP:3136040.3136060}.
\end{itemize}
